openTSNE: a modular Python library for t-SNE dimensionality reduction and embedding

### 2021-03-17 paper/cover.tex
small corrections

In the paper, we report on openTSNE, a Python-based open-source library for t-SNE visualization. openTSNE runs orders of magnitudes faster than comparable Python-based implementations (e.g., scikit-learn) and can handle data sets containing millions of data points. t-SNE has been recently criticized for poor scalability and susceptibility to batch effects. Our proposed implementation addresses these concerns and includes the lately-proposed methodological advancements, which we review in the paper's online methods section.

@@

We are submitting an original manuscript that has not been considered for publication before. Lin Tang would be an excellent choice for Editor for this manuscript because of his broad knowledge in the field and work in single-cell analytics. For reviewers, we kindly propose Dmitry Kobak (U Tuebingen), an author of recently proposed t-SNE tricks that we implemented in the library, Barbara di Camillo (U Padova), single-cell data scientists, or Cagatay Turkay (U Warwick), a specialist in explainable data visualizations.

>>>>

In the paper, we report on openTSNE, a Python-based open-source library for t-SNE. openTSNE runs orders of magnitudes faster than comparable Python-based implementations (e.g., scikit-learn) and can handle data sets containing millions of data points. t-SNE has been recently criticized for poor scalability and susceptibility to batch effects. Our proposed implementation addresses these concerns and includes the lately-proposed methodological advancements, which we review in the paper's online methods section.

@@

We are submitting an original manuscript that has not been considered for publication before. {\bf Lin Tang} would be an excellent choice for an editor for this manuscript because of her broad knowledge in the field and work in single-cell analytics. For reviewers, we kindly propose {\bf Dmitry Kobak} (U Tuebingen), an author of recently proposed t-SNE tricks that we implemented in the library, {\bf Barbara di Camillo} (U Padova), single-cell data scientists, {\bf Marinka Žitnik} (Harvard), a data integration expert, or {\bf Cagatay Turkay} (U Warwick), a specialist in explainable data visualizations.
